Effectiveness of a malaria elimination campaign

### 2017-09-06 scm.Rmd
update

---
title: "Cost-effectiveness of a malaria elimination campaign"
subtitle: "Cross-software reproducibility check"
author: "Joe Brew, Laia Cirera, Ranjeeta Thomas, Elisa Sicuri"
output:
 tufte::tufte_html: default
 tufte::tufte_handout:
   citation_package: natbib
   latex_engine: xelatex
 tufte::tufte_book:
   citation_package: natbib
   latex_engine: xelatex
bibliography: bibliography.bib
link-citations: yes
---

>>>>

---
title: "Effectiveness of a malaria elimination campaign"
subtitle: "Cross-software reproducibility check"
output:
 tufte::tufte_html: default
 tufte::tufte_handout:
   citation_package: natbib
   latex_engine: xelatex
 tufte::tufte_book:
   citation_package: natbib
   latex_engine: xelatex
bibliography: bibliography.bib
link-citations: yes
---
